Get CRediT

### 2022-10-13 scripts/r/09_credit_taxonomy.Rmd
add comments to Rmd for CRediT

contributors <- bind_rows(initiators, analysts) %>% 
  mutate(middle_name = replace_na(middle_name, ""), 
         is_initiating = if_else(surname %in% initiating_authors, 1, 0)) %>% 
  unite(name, c("firstname", "middle_name", "surname"), sep = " ") %>% 
  mutate(name = str_replace_all(name, "  ", " "))

@@

affiliations <- contributors %>% 
  count(primary_affiliation) %>% 
  arrange(n)

affiliations %>% 
  mutate(lab_truc = str_sub(primary_affiliation, 1, 30),
    lab_truc = fct_reorder(lab_truc, n, min)) %>% 
  ggplot() + 
  aes(x = n, y = lab_truc) + 
  geom_segment(aes(x = 0, xend = n, yend = lab_truc)) + 
  geom_point() + 
  labs(y = NULL) + 
  theme_bw(base_size = 9)
```

@@

initiating_names <- c("Stefano Coretta", "Joseph V. Casillas", 
                      "Simon Roessig", "Michael Franke", "Timo B. Roettger")

contributor_roles <- rev(c(
    "Conceptualization", "Data curation", "Formal Analysis",
    "Funding acquisition", "Investigation", "Methodology",
    "Project administration", "Resources", "Software", "Supervision",
    "Validation", "Visualization", "Writing - original draft",
    "Writing - review & editing"
  ))

cr_prep <- contributors %>% 
  select(name:writing_review_editing) %>% 
  pivot_longer(cols = -name, names_to = "contributor_roles", values_to = "val") %>% 
  mutate(val = as.numeric(val)) %>% 
  group_by(name, contributor_roles) %>% 
  mutate(order_x = seq_along(name)) %>% 
  group_by(name) %>% 
  mutate(order_y = seq_along(name)) %>% 
  ungroup() %>% 
  mutate(initials = gsub('\\b(\\pL)\\pL{2,}|.','\\U\\1', name, perl = TRUE), 
    is_initiating = if_else(name %in% initiating_names, 1, 0), 
    contributor_roles = fct_rev(contributor_roles))

cr_prep %>% 
  filter(is_initiating == 1) %>% 
  mutate(name = fct_relevel(name, "Stefano Coretta", "Joseph V. Casillas", 
                            "Simon Roessig", "Michael Franke")) %>% 
  ggplot() +
  aes(x = name, y = contributor_roles, alpha = val) +
    geom_point(size = 3.5, pch = 18, show.legend = F) +
    scale_x_discrete(position = "top") + 
    scale_y_discrete(labels = contributor_roles) + 
    scale_alpha_continuous(range = c(0.05, 1)) +
    labs(x = "Initiating authors", y = "Contributor roles",
         caption = "Author contributions based on CRediT taxonomy") +
    theme_minimal(base_size = 12, base_family = "Times") +
    theme(
      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
      panel.grid.minor = element_line(colour = 'grey90', size = 0.15)
    )

@@

cr_prep %>% 
  filter(is_initiating == 0) %>% 
  ggplot() +
  aes(y = initials, x = contributor_roles, alpha = val) +
    geom_point(size = 2, pch = 18, show.legend = F) +
    scale_x_discrete(position = "top", labels = rev(contributor_roles)) + 
    scale_alpha_continuous(range = c(0.05, 1)) +
    labs(x = "Contributor roles", y = "Analysts",
         caption = "Author contributions based on CRediT taxonomy") +
    theme_minimal(base_size = 12, base_family = "Times") +
    theme(
      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
      panel.grid.minor = element_line(colour = 'grey90', size = 0.15), 
      axis.text.x.top = element_text(angle = 45, hjust = 0, size = rel(0.6)), 
      axis.text.y = element_text(size = rel(0.6))
    )

>>>>

# Combine dfs in correct order
contributors <- bind_rows(initiators, analysts) %>% 
  mutate(middle_name = replace_na(middle_name, ""), 
         is_initiating = if_else(surname %in% initiating_authors, 1, 0)) %>% 
  unite(name, c("firstname", "middle_name", "surname"), sep = " ") %>% 
  mutate(name = str_replace_all(name, "  ", " "))

@@

# Get count of unique affiliations
affiliations <- contributors %>% 
  count(primary_affiliation) %>% 
  arrange(n)

# Plot affiliations as a function of n
affiliations %>% 
  mutate(lab_truc = str_sub(primary_affiliation, 1, 30),
    lab_truc = fct_reorder(lab_truc, n, min)) %>% 
  ggplot() + 
  aes(x = n, y = lab_truc) + 
  geom_segment(aes(x = 0, xend = n, yend = lab_truc)) + 
  geom_point() + 
  labs(y = NULL) + 
  theme_bw(base_size = 9)
```

@@

# Vector of formated contributor roles
contributor_roles <- c(
    "Conceptualization", "Data curation", "Formal Analysis",
    "Funding acquisition", "Investigation", "Methodology",
    "Project administration", "Resources", "Software", "Supervision",
    "Validation", "Visualization", "Writing - original draft",
    "Writing - review & editing"
  )

# Format contributors for plotting
cr_prep <- contributors %>% 
  select(name:writing_review_editing, is_initiating) %>% 
  pivot_longer(
    cols = -c("name", "is_initiating"), 
    names_to = "contributor_roles", 
    values_to = "val"
    ) %>% 
  mutate(val = as.numeric(val)) %>% 
  group_by(name, contributor_roles) %>% 
  mutate(order_x = seq_along(name)) %>% 
  group_by(name) %>% 
  mutate(order_y = seq_along(name)) %>% 
  ungroup() %>% 
  mutate(initials = gsub('\\b(\\pL)\\pL{2,}|.','\\U\\1', name, perl = TRUE), 
    contributor_roles = fct_rev(contributor_roles))

# Plot initiating authors
cr_prep %>% 
  filter(is_initiating == 1) %>% 
  mutate(name = fct_relevel(name, "Stefano Coretta", "Joseph V. Casillas", 
                            "Simon Roessig", "Michael Franke")) %>% 
  ggplot() +
  aes(x = name, y = contributor_roles, alpha = val) +
    geom_point(size = 3.5, pch = 18, show.legend = F) +
    scale_x_discrete(position = "top") + 
    scale_y_discrete(limits = rev, labels = rev(contributor_roles)) + 
    scale_alpha_continuous(range = c(0.05, 1)) +
    labs(x = "Initiating authors", y = "Contributor roles",
         caption = "Author contributions based on CRediT taxonomy") +
    theme_minimal(base_size = 12, base_family = "Times") +
    theme(
      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
      panel.grid.minor = element_line(colour = 'grey90', size = 0.15)
    )

@@

cr_prep %>% 
  filter(is_initiating == 0) %>% 
  ggplot() +
  aes(y = initials, x = contributor_roles, alpha = val) +
    geom_point(size = 1.75, pch = 18, show.legend = F) +
    scale_x_discrete(labels = contributor_roles) + 
    scale_alpha_continuous(range = c(0.05, 1)) +
    labs(x = NULL, y = "Analysts",
         caption = "Contributor roles\nAuthor contributions based on CRediT taxonomy") +
    theme_minimal(base_size = 12, base_family = "Times") +
    theme(
      axis.title.y = element_text(size = rel(.9), hjust = 0.95),
      axis.title.x = element_text(size = rel(.9), hjust = 0.95),
      panel.grid.major = element_line(colour = 'grey90', size = 0.15),
      panel.grid.minor = element_line(colour = 'grey90', size = 0.15), 
      axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, 
                                     size = rel(0.6)), 
      axis.text.y = element_text(size = rel(0.5))
    )
